Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
wordings

%------------------------------------
\subsection{Overview of the Synthesis Process using DSVerifier}
\label{verification-flow}
%------------------------------------

@@

An overview of the synthesis process is illustrated in
Fig.~\ref{DSVerifier_process}; a detailed description of DSVerifier tool can
be found in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
user/synthesiser and Steps A to D are automatically performed by DSVerifier.
%
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{Synthesis process using DSVerifier and the CBMC CEGIS module.}
\label{DSVerifier_process}
\end{figure*}

>>>>

%------------------------------------
\subsection{Overview of the Synthesis Process}
\label{verification-flow}
%------------------------------------

@@

The synthesis process is illustrated in Fig.~\ref{DSVerifier_process}. 
A~detailed description of DSVerifier tool can be found
in~\cite{IsmailBCFF15}.  Steps $1$ to $5$ are performed by the
user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
%
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{Overview of the synthesis process\label{DSVerifier_process}}
\end{figure*}
